\begin{frame}{Jasmine is confirmed --- cold $\gg$ heat burden}
  \footnotesize
  \textbf{Jingwen Liu et al.\ (2020)}\\
  \emph{Cause-specific mortality attributable to cold and hot ambient temperatures
  in Hong Kong: a time-series study, 2006--2016}.\\
  \textit{Sustainable Cities and Society} 57:102131.\\
  DOI: \texttt{10.1016/j.scs.2020.102131}.

  \vspace{0.55em}
  \renewcommand{\arraystretch}{1.18}
  \begin{tabular}{@{}p{0.34\textwidth}p{0.25\textwidth}p{0.25\textwidth}@{}}
    \toprule
    \textbf{Attributable fraction} & \textbf{Cold / moderate} & \textbf{Heat / extreme} \\
    \midrule
    Thermal side & \textbf{Cold 4.72\%} & Heat 0.16\% \\
    Intensity class & \textbf{Moderate 4.25\%} & Extreme 0.63\% \\
    \bottomrule
  \end{tabular}

  \vspace{0.5em}
  \callout{Daily mortality; DLNM $+$ quasi-Poisson; reversed J-shaped curve.
  Extreme cold had the highest risk: injury RR 2.18 (1.03--4.62), lag 0--21.}
\end{frame}

\begin{frame}{One team evidence chain}
  \scriptsize
  \begin{center}
    \begin{tikzpicture}[
      node distance=0.46cm,
      box/.style={
        fill=LaidlawSoft,
        draw=LaidlawGray,
        rounded corners=2pt,
        text width=0.26\textwidth,
        align=center,
        inner sep=6pt
      }
    ]
      \node[box] (jasmine) {\textbf{Jasmine}\\Liu et al.\ 2020\\daily mortality RR / AF\\2006--2016};
      \node[box, right=of jasmine] (roro) {\textbf{Roro}\\Liu et al.\ 2026\\excess heat deaths\\2014--2023};
      \node[box, right=of roro] (stroke) {\textbf{Our extension}\\monthly stroke aggregates\\paired hot / cold\\2013--2023};
      \draw[-{Latex[length=2mm]},LaidlawTeal] (jasmine) -- node[above,align=center] {local RRs} (roro);
      \draw[-{Latex[length=2mm]},LaidlawTeal] (roro) -- node[above,align=center] {team baseline} (stroke);
    \end{tikzpicture}
  \end{center}

  \vspace{0.4em}
  \textbf{Roro paper:} Zhenyuan Liu, Chao Ren, Jingwen Liu,
  Kawasaki Yurika and David Makram Bishai.\\
  DOI: \texttt{10.64898/2026.03.05.26347683} (medRxiv v1).

  \vspace{0.4em}
  \callout{Roro estimates 1,455 (1,098--1,812) to 3,238 (3,234--3,242)
  excess deaths across four heatwave definitions. Complementarity, not competition.}
\end{frame}

\begin{frame}{Roro's four-definition mortality baseline}
  \scriptsize
  \renewcommand{\arraystretch}{1.15}
  \begin{tabular}{@{}p{0.20\textwidth}p{0.50\textwidth}p{0.20\textwidth}@{}}
    \toprule
    \textbf{Definition} & \textbf{Event / lag intent} & \textbf{RR source} \\
    \midrule
    HWD\_Tavg & Mean T at 99th percentile (30.60\,$^\circ$C);
      20-day window; lag phases 0, 1--5, 6--21 & Jasmine \\
    HWD\_Tmax & Consecutive very hot days; $T_{\max}\geq33^\circ$C & Wang / Ren \\
    HWD\_Tmin & Consecutive hot nights; $T_{\min}\geq28^\circ$C & Wang / Ren \\
    HWD\_Tcombined & 2 hot days $+$ 3 hot nights (2D3N);
      event $+$ five later days & Wang / Ren \\
    \bottomrule
  \end{tabular}

  \vspace{0.55em}
  \callout{The Mac \texttt{revised manuscript\_clean.pdf} is not yet ingested.
  This is the medRxiv v1 baseline; exact run operators still need a source manifest.}
\end{frame}

\begin{frame}{Definition-harmonised extension through 2023}
  \footnotesize
  \begin{enumerate}
    \item Ingest Jasmine's full PDF / supplement; lock reference, knots, lags and test universe.
    \item Reconstruct daily hot and cold definitions without opening stroke associations.
    \item Audit coding in the shared 2013--2016 window.
    \item Apply unchanged definitions through December 2023.
    \item Collapse daily burden to month; join to Roro's \textbf{true stroke-event month}.
    \item Report exposed months, estimates and intervals; keep null counts secondary.
  \end{enumerate}

  \vspace{0.45em}
  \callout{Daily mortality AF $\neq$ modelled excess deaths $\neq$ monthly stroke association.
  This is definition transport, not an exact replication.}
\end{frame}

\begin{frame}{Next week: symmetric hot and cold months}
  \footnotesize
  \begin{columns}[T]
    \begin{column}{0.47\textwidth}
      {\color{LaidlawTeal}\textbf{Hot families (HM)}}
      \begin{itemize}
        \item HKO hot nights / very hot days
        \item Monthly percentile tails
        \item VHD, HN and 2D3N spells
        \item Heatwave starts and event days
        \item Degree-day intensity
        \item Anomaly, compound, onset, warnings
      \end{itemize}
    \end{column}
    \begin{column}{0.47\textwidth}
      {\color{LaidlawTeal}\textbf{Cold families (CM)}}
      \begin{itemize}
        \item HKO cold-day counts
        \item 12\,$^\circ$C and 10\,$^\circ$C sensitivities
        \item Monthly percentile tails
        \item Cold spells and event counts
        \item Cold degree-day intensity
        \item Flu, anomaly, warning, onset
      \end{itemize}
    \end{column}
  \end{columns}

  \vspace{0.4em}
  \callout{Catalogue: 50 HM definitions, 48 CM definitions,
  and paired pathways H01--H12 / C01--C12.}
\end{frame}

\begin{frame}{Starter HM / CM set --- run exposure audits first}
  \scriptsize
  \renewcommand{\arraystretch}{1.12}
  \begin{tabular}{@{}p{0.10\textwidth}p{0.34\textwidth}p{0.10\textwidth}p{0.34\textwidth}@{}}
    \toprule
    \textbf{Hot} & \textbf{Rule} & \textbf{Cold} & \textbf{Rule} \\
    \midrule
    HM23 & Hogan p90 heatwave-count month & CM03 & $\geq5$ days with $T_{\min}\leq12^\circ$C \\
    HM08 & Monthly mean temperature $\geq$p90 & CM08 & Monthly mean temperature $\leq$p05 \\
    HM15 & Touches a 5-VHD spell & CM15 & Touches a 3-day cold spell \\
    HM17 & Touches a 5-HN spell & CM05 & Any $T_{\min}\leq10^\circ$C day \\
    HM19 & Touches a 2D3N event & CM30 & Cold $+$ influenza sensitivity \\
    \bottomrule
  \end{tabular}

  \vspace{0.55em}
  \footnotesize
  First-wave intensity / compound additions: HM27 night heat-degree burden and
  HM32 hot $+$ O$_3$. Freeze thresholds, selected months and missingness before outcomes.
\end{frame}

\begin{frame}{Hogan's atmospheric recipe is one HM family}
  \footnotesize
  \begin{center}
    \begin{tikzpicture}[
      node distance=0.55cm,
      box/.style={
        fill=LaidlawSoft,
        draw=LaidlawGray,
        rounded corners=2pt,
        text width=0.25\textwidth,
        align=center,
        inner sep=6pt
      }
    ]
      \node[box] (event) {Li et al.\\May--September\\$T_{\max}>$ calendar-day p90\\$\geq3$ consecutive days};
      \node[box, right=of event] (count) {Hogan adaptation\\count event starts\\within each month};
      \node[box, right=of count] (tail) {Flag upper-tail\\monthly counts\\HM23 / HM24};
      \draw[-{Latex[length=2mm]},LaidlawTeal] (event) -- (count);
      \draw[-{Latex[length=2mm]},LaidlawTeal] (count) -- (tail);
    \end{tikzpicture}
  \end{center}

  \vspace{0.55em}
  Li C et al., \emph{Atmospheric Research} 315 (2025) 107845.\\
  DOI: \texttt{10.1016/j.atmosres.2024.107845}.

  \vspace{0.35em}
  \callout{Named and credited --- beside HKO counts, Jasmine transport,
  Roro / Wang--Ren definitions, percentiles and cold counterparts.}
\end{frame}

\begin{frame}{Gene / \textasciitilde{}10\,$^\circ$C: hypothesis only}
  \footnotesize
  \begin{itemize}
    \item Discussion idea: South China populations may appear relatively heat-adapted,
      while temperatures around \textasciitilde{}10\,$^\circ$C may remain consequential.
    \item This ecological monthly study cannot identify genes, ancestry effects
      or causal adaptation.
    \item Housing, cooling, behavior, occupation, age, health care and acclimatization
      remain alternative explanations.
    \item The 10\,$^\circ$C rule is a candidate CM sensitivity, not a biological cutoff.
    \item No stroke findings yet; synthetic outputs are not findings.
  \end{itemize}

  \vspace{0.55em}
  \callout{Small asks: source-table lock with Dr Bishai, weather-definition lock with Hogan,
  and true-event-month lock with Roro :)}
\end{frame}
