\documentclass[11pt,a4paper]{article}

\usepackage[a4paper,margin=1.25cm]{geometry}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage[table]{xcolor}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{array}
\usepackage{enumitem}
\usepackage{amssymb}

\definecolor{LaidlawNavy}{HTML}{1B2A41}
\definecolor{LaidlawTeal}{HTML}{3D6B6E}
\definecolor{LaidlawRust}{HTML}{A85A3A}
\definecolor{LaidlawGray}{HTML}{E8EAED}
\definecolor{LaidlawSoft}{HTML}{F4F6F8}
\definecolor{LaidlawText}{HTML}{2C2C2C}

\color{LaidlawText}
\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}
\setlist[itemize]{leftmargin=1.35em,itemsep=0.18em,topsep=0.15em}
\newcolumntype{Y}{>{\raggedright\arraybackslash}X}
\newcommand{\sectionline}[1]{%
  \vspace{0.45em}{\color{LaidlawTeal}\bfseries #1}\par
  \vspace{0.15em}\color{LaidlawGray}\hrule\color{LaidlawText}\vspace{0.35em}}
\newcommand{\decision}[2]{%
  \(\square\)\ \textbf{#1} #2\par
  \hspace{1.5em}{\color{LaidlawGray}\rule{0.91\linewidth}{0.35pt}}\vspace{0.28em}\par}

\begin{document}

\begin{minipage}[t]{0.72\textwidth}
  {\fontsize{17}{19}\selectfont\color{LaidlawNavy}\bfseries
  Locking the weather definitions with Hogan}\par
  \vspace{0.2em}
  {\color{LaidlawTeal}\bfseries Tuesday 28 July 2026 \(\cdot\) 55 minutes}
\end{minipage}
\hfill
\begin{minipage}[t]{0.25\textwidth}
  \raggedleft
  \colorbox{LaidlawSoft}{\parbox{0.88\linewidth}{\centering\footnotesize
  \textbf{Bishai Lab}\\Laidlaw HK thermal--stroke}}
\end{minipage}

\vspace{0.45em}
\colorbox{LaidlawSoft}{%
  \parbox{\dimexpr\textwidth-2\fboxsep\relax}{\normalsize
  \textbf{\color{LaidlawNavy}Purpose.}
  Listen first, then leave with a written exposure specification agreed with
  Hogan before Gate~3. The graphs are exposure-only checks; there are no stroke
  findings or coefficients yet.}}

\begin{minipage}[t]{0.60\textwidth}
  \raggedright
  \sectionline{Six decisions to write down}
  \small
  \decision{Li-HW / HM23.}{Season (May--Sep?); calendar-day
  \(T_{\max}\) p90 reference and tie rule; 15-day window; \(\geq3\) days;
  gap rule; cross-month start vs touch/burden.}

  \decision{Gate 3 pair.}{Choose one hot and one cold co-primary.}

  \decision{Roro siblings.}{Name \texttt{HWD\_Tavg},
  \texttt{HWD\_Tmax}, \texttt{HWD\_Tmin}, and
  \texttt{HWD\_Tcombined} as monthly exposure siblings? Mortality RRs are
  not stroke coefficients.}

  \decision{Reference freeze.}{2013--2019, full 2013--2023, or a defensible
  pre-study/external climatology?}

  \decision{CM05.}{Keep any \(T_{\min}\leq10^\circ\)C day as a
  severe-cold sensitivity, not biology.}

  \decision{Age visibility.}{Show 65--69 and 70--74 if Roro's approved
  aggregates and disclosure controls allow.}
\end{minipage}
\hfill
\begin{minipage}[t]{0.375\textwidth}
  \sectionline{Starter HM / CM set}
  \footnotesize
  \renewcommand{\arraystretch}{1.12}
  \begin{tabularx}{\linewidth}{@{}>{\bfseries}lY>{\bfseries}lY@{}}
    \toprule
    \multicolumn{2}{c}{\color{LaidlawRust}Hot} &
    \multicolumn{2}{c}{\color{LaidlawTeal}Cold} \\
    \midrule
    HM23 & Li-HW count p90 & CM03 & 5 cold days \\
    HM08 & monthly mean p90 & CM08 & monthly mean p05 \\
    HM15 & 5 hot-day spell & CM15 & 3 cold-day spell \\
    HM17 & 5 hot-night spell & CM05 & any \(\leq10^\circ\)C day \\
    HM19 & 2D3N window & CM30 & cold + influenza \\
    HM27 & night heat-degree & & \\
    HM32 & heat + ozone & & \\
    \bottomrule
  \end{tabularx}

  \sectionline{55-minute flow}
  \small
  \begin{tabularx}{\linewidth}{@{}>{\bfseries\color{LaidlawNavy}}lX@{}}
    0--10 & Hogan frames the question; Bob listens. \\
    10--17 & Jasmine + Roro + monthly stroke estimands. \\
    17--32 & Lock Li-HW \(\rightarrow\) HM23. \\
    32--42 & Co-primary pair + Roro siblings. \\
    42--49 & Age bands and handoffs. \\
    49--55 & Read back written decisions. \\
  \end{tabularx}

  \sectionline{Meeting rule}
  \small
  Put choices on the table; do not ask Hogan to approve a finished answer.
  Record his wording and circulate it to Hogan and Roro for correction.
\end{minipage}

\sectionline{Notes / unresolved items}
{\color{LaidlawGray}
\rule{\linewidth}{0.35pt}\\[1.45em]
\rule{\linewidth}{0.35pt}\\[1.45em]
\rule{\linewidth}{0.35pt}\\[1.45em]
\rule{\linewidth}{0.35pt}\\[1.45em]
\rule{\linewidth}{0.35pt}}

\vfill
\colorbox{LaidlawNavy}{%
  \parbox{\dimexpr\textwidth-2\fboxsep\relax}{\centering\footnotesize\color{white}
  \textbf{Credit:} Hogan leads weather framing and the Li-event
  count-to-upper-tail monthly adaptation; Roro leads governed stroke outcomes
  and true-event timing; Jingwen Liu et al.\ (2020) and Zhenyuan Liu et al.\
  (2026) anchor the mortality evidence family.}}

\end{document}
